Look at the phylum level

### 2019-11-05 scripts/19_phylum_table.Rmd
the correlation

```{r}
phy %>% 
  gather(key = 'Sampleid', value = 'relab', names(.)[2]: names(.)[ncol(.)]) %>% 
  left_join(pheno, by = 'Sampleid') %>% 
  filter(ID == 'Bacteroidetes') %>% 
  select(ID, relab, Toxicity) %>% 
  ggboxplot(x = 'Toxicity', y = 'relab', color = 'Toxicity', palette  = 'lancet', add = 'jitter')   + 
  stat_compare_means()
```

```{r}
phy %>% 
  gather(key = 'Sampleid', value = 'relab', names(.)[2]: names(.)[ncol(.)]) %>% 
  left_join(pheno, by = 'Sampleid') %>% 
  filter(ID == 'Firmicutes') %>% 
  select(ID, relab, Toxicity) %>% 
  ggboxplot(x = 'Toxicity', y = 'relab', color = 'Toxicity', palette  = 'lancet', add = 'jitter')   + 
  stat_compare_means()  
```

>>>>

```{r}
phy %>% 
  gather(key = 'Sampleid', value = 'relab', names(.)[2]: names(.)[ncol(.)]) %>% 
  left_join(pheno, by = 'Sampleid') %>% 
  filter(ID == 'Bacteroidetes') %>% 
  select(ID, relab, Toxicity) %>% 
  ggboxplot(x = 'Toxicity', y = 'relab', color = 'Toxicity', palette  = 'lancet', add = 'jitter')   + 
  stat_compare_means()+
  ggsave('../figs/phylum_abundance_Bacteroidetes.jpg')
```

```{r}
phy %>% 
  gather(key = 'Sampleid', value = 'relab', names(.)[2]: names(.)[ncol(.)]) %>% 
  left_join(pheno, by = 'Sampleid') %>% 
  filter(ID == 'Firmicutes') %>% 
  select(ID, relab, Toxicity) %>% 
  ggboxplot(x = 'Toxicity', y = 'relab', color = 'Toxicity', palette  = 'lancet', add = 'jitter')   + 
  stat_compare_means()  +
  ggsave('../figs/phylum_abundance_Firmicutes.jpg')
```
